\documentclass{resume} % Use the custom resume.cls style

\usepackage{hyperref}
\usepackage[left=0.50in,top=0.5in,right=0.50in,bottom=0.5in]{geometry} % Document margins


%----------------------------------------------------------------------------------------
%   NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\name{Conner DiPaolo} % Your name at the top

\address{\textrm{\url{http://dipaolo.xyz}} -- \textsf{\url{cdipaolo96@gmail.com}} -- \textsf{(949) 300 3774}}

\begin{document}
 
%----------------------------------------------------------------------------------------
%   PROFESSIONAL EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\vspace{-1em}
\begin{rSection}{EXPERIENCE}


\begin{rSubsection}{Citadel -- {\it Chicago, IL}}{January 2021 - Present}{Business Manager -- {\sl Global Quantitative Strategies}}

\item[]
\vspace{-2em}

\end{rSubsection}

\begin{rSubsection}{Yelp -- {\it San Francisco, CA}}{June 2019 - January 2021}{Applied Scientist -- {\sl Pricing and Revenue Optimization}}

\item Designed and implemented the experimental treatment within a project expanding off-Yelp advertiser audiences, reducing Yelp's cost per advertising click by $>$35\% and fulfilling $>$15\% more budget.

\item Proposed and led an effort to collect randomized price recommendation data for Yelp's advertising product, facilitating training an uplift (RL) model for dynamic pricing now worth millions of dollars in yearly revenue.

\item Initiated and led a company-wide transition towards more efficient statistical estimators to measure subscriber retention and revenue, which decreased A/B test runtime by 15 days (12-16\% faster than the status quo.)

\end{rSubsection}

\begin{rSubsection}{Jet Propulsion Lab -- {\it Pasadena, CA}}{June 2018 - August 2018}{Research Intern -- {\sl Deep Space Optical Communications}}

\item Mathematically developed improved statistical algorithms for ground communications receiver control which are currently implemented in hardware and slated to join the 2022 Psyche mission to an asteroid near Mars.
\end{rSubsection}

\begin{rSubsection}{Yelp -- {\it San Francisco, CA}}{May 2017 - August 2017}{Machine Learning Intern -- {\sl Advertisement Optimization}}

\item Architected and productionized a deep learning model used to select between millions of advertisement photos.
\item Generated a statistically significant 4.5\% lift in advertisement click-through rate over status quo photo selection.
\end{rSubsection}

\begin{rSubsection}{Yelp -- {\it San Francisco, CA}}{May 2016 - August 2016}{Machine Learning Intern -- {\sl Spam Detection}}

\item Increased out-of-sample Matthews Correlation of a spam detection model by 25.7\% over the status quo model on points detected by humans as `difficult to classify' by running a principled model search.
\item Primary author of a service marshalling over 350,000 Kafka messages/day into MySQL tables for four teams.
\end{rSubsection}

\vspace{-0.5em}
\end{rSection}

%----------------------------------------------------------------------------------------
%   PULICATIONS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PUBLICATIONS}

\begin{rSubsection}{A Randomized Algorithm for Preconditioner Selection}{\textsf{arxiv.org/abs/1908.00633}}{By Conner DiPaolo and Weiqing Gu. Pre-print. August 2019.}

\item Created state-of-the-art preconditioned solver for kernel regression using our preconditioner selection algorithm.
\end{rSubsection}

\begin{rSubsection}{Signal Intensity Deconvolution in Optical Receivers}{\textsf{doi.org/10.1109/LCOMM.2019.2912382}}{By Conner DiPaolo and Ryan Rogalin. IEEE Communications Letters. July 2019.}

\item Developed the first consistent algorithm for estimating the center of a discretized communications beam.

\end{rSubsection}

\vspace{-0.5em}
\end{rSection}

%----------------------------------------------------------------------------------------
%   OPEN SOURCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{OPEN SOURCE}

\begin{rSubsection}{GOML}{\textsf{github.com/cdipaolo/goml}}{Creator - Second most starred Golang machine learning library on Github with $> 1,000$ stars.}

\item[]
\vspace{-2.5em}

\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%   SKILLS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{SKILLS}

\textbf{Programming Languages:} Python, SQL, R, Golang, Matlab\\[0em]
\textbf{Tools \& Technologies:} Numpy, SciPy, Pandas, Apache Spark, Redshift, Git, SciKit-Learn, PyTorch

\end{rSection}

%----------------------------------------------------------------------------------------
%   EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{EDUCATION}

{{\bf Harvey Mudd College} -- {\it B.S. Mathematics with Departmental Honors}} \hfill {\em 3.84 GPA, 3.88 In-Major GPA}\\[-1.75em]

\end{rSection}

\end{document}
